---
title: "Breast Gene Burden Testing Analysis Report"
author: "Jenny Li"
output: 
  html_document:
    theme: paper
    toc: true
    toc_float: true
    code_folding: hide
date: "`r Sys.Date()`"
---

<!-- 
GENE BURDEN TESTING NOTES:
- M1 = pathogenic variants only (LoF level 1)
- M2 = VUS variants only (LoF level 2) 
- M3 = pathogenic + VUS variants combined
- ADD = additive burden test (use for BETA interpretation)
- SKAT/SKATO = other burden tests (not used in this report)
- Gene-based significance thresholds vary by correction method

KEY TERMS:
- BETA (Effect Size): Log odds ratio for gene burden
  * Positive BETA = gene variants increase disease risk
  * Negative BETA = gene variants are protective
- OR (Odds Ratio): exp(BETA) - easier interpretation than log odds
- SE (Standard Error): Uncertainty around effect size
- PVAL_ADJ/FDR: False discovery rate-adjusted p-values (Benjamini-Hochberg)
- PVAL_BONF: Bonferroni-corrected p-values (more conservative)
-->

params:
  gene_based_file: "ALL_step2_gene_genome.regenie"
  pheno_file: "phenotype_regenie.txt"
  report_title: "Breast_Gene_Burden"

```{r setup,echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 6)
library(dplyr)
library(readr)
library(data.table)
library(ggplot2)
library(knitr)
library(kableExtra)
library(ggrepel)

# Set consistent theme
theme_set(theme_minimal(base_size = 12))
```

```{r load-data,echo=FALSE,message=FALSE,warning=FALSE}
# Set file paths with fallbacks
gene_based_file <- if(exists("params")) params$gene_based_file else "step2_gene_based_STATUS.regenie"
pheno_file <- if(exists("params")) params$pheno_file else "TECAC_WES.regenie.pheno.txt"

# Load gene-based data
gene_based <- read_delim(gene_based_file, delim = " ", col_names = TRUE, trim_ws = TRUE, skip = 1) %>%
  mutate(across(c(CHROM, GENPOS, N, N_CASES, N_CONTROLS), as.integer),
         across(c(A1FREQ, A1FREQ_CASES, A1FREQ_CONTROLS, BETA, SE, CHISQ, LOG10P), as.numeric)) %>%
  mutate(CHROM = as.factor(CHROM),
         PVAL = 10^(-LOG10P),
         PVAL_ADJ = p.adjust(PVAL, method = "BH"),
         LOG10P_ADJ = -log10(PVAL_ADJ),
         PVAL_BONF = pmin(PVAL * n(), 1),
         LOG10P_BONF = -log10(PVAL_BONF),
         OR = exp(BETA)) %>%
  # Extract gene and mask information from ID column
  mutate(
    GENE = sub("\\..*", "", ID),
    MASK = sub(".*\\.(M[0-9]+).*", "\\1", ID),
    THRESH = sub(".*\\.(\\d+\\.\\d+)$", "\\1", ID)
  ) %>%
  # Filter to ADD test only for BETA-based analysis
  filter(TEST == "ADD")

# Load phenotype data
pheno <- read_delim(pheno_file, delim = " ", col_names = TRUE, trim_ws = TRUE)
```

## Analysis Summary

```{r summary-stats,echo=FALSE,message=FALSE,warning=FALSE}
# Build proper summary table with scalar values
summary_df <- data.frame(
  Metric = c("Total Samples", "Cases", "Controls", 
             "Genes Tested (Burden Test)", "Total Gene-Mask Tests"),
  Count = c(
    length(unique(pheno$IID)),
    sum(pheno$STATUS == 1),
    sum(pheno$STATUS == 0),
    length(unique(gene_based$GENE)),  # important: gene count, not row count
    nrow(gene_based)
  )
)

kable(summary_df, format = "html", col.names = c("Metric", "Count")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, bold = TRUE)
```

## Multiple Testing Correction Summary

```{r correction-summary,echo=FALSE,message=FALSE,warning=FALSE}
# Compare correction methods
correction_comparison <- data.frame(
  Method = c("Uncorrected (p < 0.05)", "BH/FDR (q < 0.05)", "Bonferroni (p < 0.05)"),
  Significant_Tests = c(
    sum(gene_based$PVAL < 0.05, na.rm = TRUE),
    sum(gene_based$PVAL_ADJ < 0.05, na.rm = TRUE),
    sum(gene_based$PVAL_BONF < 0.05, na.rm = TRUE)
  ),
  Total_Tests = rep(nrow(gene_based), 3)
) %>%
mutate(Significance_Rate = round(Significant_Tests / Total_Tests * 100, 2))

kable(correction_comparison, format = "html", digits = 2,
      col.names = c("Correction Method", "Significant Tests", "Total Tests", "Rate (%)")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, bold = TRUE)
