---
title: "`r params$report_title`"
author: "`r params$author`"
output: 
  html_document:
    theme: paper
    toc: true
    toc_float: true
    code_folding: hide
date: "`r Sys.Date()`"
params:
  project: "PROJECT"
  input_dir: "output"
  output_dir: "reports"
  pheno_file: "input/PROJECT.regenie.pheno.txt"
  single_variant_pattern: "PROJECT.chr{CHR}.step2_single_variant_STATUS.regenie"
  gene_based_pattern: "PROJECT.chr{CHR}.step2_gene_based_STATUS.regenie"
  report_title: "REGENIE Exome-Wide Association Analysis Report"
  author: "Analysis Report"
  exome_sig_threshold: 2.5e-6
  fdr_threshold: 0.05
---

**Note:** This report is configured for Exome-Wide Association Studies (ExWAS) using Regenie burden and single-variant results.

<!-- 
NOTES TO SELF:
- M1 = pathogenic variants only (LoF level 1)
- M2 = pathogenic + VUS variants combined (LoF level 1 & 2)
- ADD = additive burden test (use for BETA interpretation)
- SKAT/SKATO = other burden tests (not used in this report)
- Exome-wide significance = p < 2.5e-6 (not GWAS 5e-8)
- Lambda GC less interpretable in ExWAS due to sparse rare variants

KEY TERMS:
- BETA (Effect Size): Log odds ratio of disease association for alt allele
  * Positive BETA = alt allele increases disease risk
  * Negative BETA = alt allele is protective
- SE (Standard Error): Uncertainty around effect size estimate
  * High SE = less confidence in BETA (common for rare variants)
- PVAL/LOG10P: p-value from association test
  * LOG10P = -log10(p-value) for plotting
  * Smaller p-values (larger LOG10P) = stronger evidence
- PVAL_ADJ/FDR: False discovery rate-adjusted p-values (Benjamini-Hochberg)
  * Controls for multiple testing across thousands of variants/genes
  * Prevents false positives from testing many hypotheses
-->
```{r setup, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 6)
library(dplyr)
library(readr)
library(data.table)
library(ggplot2)
library(knitr)
library(kableExtra)
library(ggrepel)
library(qqman)

# Set consistent theme
theme_set(theme_minimal(base_size = 12))

# Create output directory if it doesn't exist
if(!dir.exists(params$output_dir)) {
  dir.create(params$output_dir, recursive = TRUE)
}
```
```{r load-data, echo=FALSE, message=FALSE, warning=FALSE}
# Validate parameters
if(is.null(params$project) || params$project == "") {
  stop("ERROR: project parameter is required")
}

cat("Project:", params$project, "\n")
cat("Input directory:", params$input_dir, "\n")

# Calculate exome-wide significance threshold
exome_sig_log10p <- -log10(params$exome_sig_threshold)

# Build file paths from patterns
single_variant_files <- sapply(1:22, function(chr) {
  pattern <- gsub("\\{CHR\\}", chr, params$single_variant_pattern)
  file.path(params$input_dir, pattern)
})

gene_based_files <- sapply(1:22, function(chr) {
  pattern <- gsub("\\{CHR\\}", chr, params$gene_based_pattern)
  file.path(params$input_dir, pattern)
})

# Load single variant data from all chromosomes
single_variant_list <- list()

for(i in 1:22) {
  if(file.exists(single_variant_files[i])) {
    single_variant_list[[i]] <- read_delim(single_variant_files[i], delim = " ", 
                                           col_names = TRUE, trim_ws = TRUE,
                                           show_col_types = FALSE)
  }
}

# Combine all single variant data
if(length(single_variant_list) > 0) {
  single_variant <- bind_rows(single_variant_list) %>%
    mutate(across(c(CHROM, GENPOS, N, N_CASES, N_CONTROLS), as.integer),
           across(c(A1FREQ, A1FREQ_CASES, A1FREQ_CONTROLS, BETA, SE, CHISQ, LOG10P), as.numeric)) %>%
    mutate(CHROM = as.factor(CHROM)) %>% 
    arrange(CHROM, GENPOS) %>% 
    mutate(PVAL = 10^(-LOG10P),
           PVAL_ADJ = p.adjust(PVAL, method = "BH"),
           LOG10P_ADJ = -log10(PVAL_ADJ),
           POS_INDEX = row_number(),
           OR = exp(BETA))
} else {
  stop("No single variant files found!")
}

cat("Total single variants loaded:", nrow(single_variant), "\n")

# Load gene-based data from all chromosomes
gene_based_list <- list()

for(i in 1:22) {
  if(file.exists(gene_based_files[i])) {
    gene_based_list[[i]] <- read_delim(gene_based_files[i], delim = " ", 
                                       col_names = TRUE, trim_ws = TRUE, skip = 1,
                                       show_col_types = FALSE)
  }
}

# Combine all gene-based data
if(length(gene_based_list) > 0) {
    gene_based <- bind_rows(gene_based_list) %>%
        mutate(across(c(CHROM, GENPOS, N, N_CASES, N_CONTROLS), as.integer),
               across(c(A1FREQ, A1FREQ_CASES, A1FREQ_CONTROLS, BETA, SE, CHISQ, LOG10P), as.numeric)) %>%
        mutate(CHROM = as.factor(CHROM),
               PVAL = 10^(-LOG10P),
               PVAL_ADJ = p.adjust(PVAL, method = "BH"),
               LOG10P_ADJ = -log10(PVAL_ADJ),
               OR = exp(BETA)) %>%
        # Extract gene and mask information from ID column
        mutate(
            GENE = sub("\\..*", "", ID),
            MASK = sub(".*\\.(M[0-9]+).*", "\\1", ID),
            THRESH_RAW = sub(".*\\.(.*)$", "\\1", ID),
            THRESH = ifelse(grepl("^\\d+\\.\\d+$", THRESH_RAW), as.numeric(THRESH_RAW),
                           ifelse(THRESH_RAW == "all", "All variants", THRESH_RAW))
        ) %>%
        # Filter to ADD test only
        filter(TEST == "ADD")
} else {
    stop("No gene-based files found!")
}

cat("Total gene-based tests loaded:", nrow(gene_based), "\n")
```

## Analysis Summary

**Project:** `r params$project`
```{r summary-stats, echo=FALSE, message=FALSE, warning=FALSE}
# Load phenotype file for actual case/control numbers
if(file.exists(params$pheno_file)) {
  pheno <- read_delim(params$pheno_file, delim = " ", col_names = TRUE, 
                      trim_ws = TRUE, show_col_types = FALSE)
} else {
  stop("Phenotype file not found: ", params$pheno_file)
}

# Build proper summary table with scalar values
summary_df <- data.frame(
  Metric = c("Total Samples", "Cases", "Controls", 
             "Variants Tested (Single-Variant)", 
             "Genes Tested (Burden Test)"),
  Count = c(
    length(unique(pheno$IID)),
    sum(pheno$STATUS == 1, na.rm = TRUE),
    sum(pheno$STATUS == 0, na.rm = TRUE),
    nrow(single_variant),
    length(unique(gene_based$GENE))
  )
)

kable(summary_df, format = "html", col.names = c("Metric", "Count")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, bold = TRUE)
```

## Quality Metrics
```{r quality-metrics, echo=FALSE, message=FALSE, warning=FALSE}
# Calculate lambda GC for both analyses
single_lambda <- median(qchisq(1 - single_variant$PVAL, 1), na.rm = TRUE) / qchisq(0.5, 1)
gene_lambda <- median(qchisq(1 - gene_based$PVAL, 1), na.rm = TRUE) / qchisq(0.5, 1)

# Simple quality metrics
quality_df <- data.frame(
    Metric = c(
        paste0("Significant Single-Variants (p < ", params$exome_sig_threshold, ")"),
        paste0("Significant Gene-Based (FDR < ", params$fdr_threshold, ")"),
        "Lambda GC (Single-Variant)",
        "Lambda GC (Gene-Based)",
        "Max Effect Size (Gene-Based OR)"
    ),
    Value = c(
        format(sum(single_variant$LOG10P > exome_sig_log10p, na.rm = TRUE), big.mark = ","),
        format(sum(gene_based$PVAL_ADJ < params$fdr_threshold, na.rm = TRUE), big.mark = ","),
        round(single_lambda, 3),
        round(gene_lambda, 3),
        round(max(exp(gene_based$BETA[gene_based$PVAL_ADJ < params$fdr_threshold]), na.rm = TRUE), 2)
    )
)

kable(quality_df, format = "html",
      col.names = c("Quality Metric", "Value")) %>%
    kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = TRUE)
```

## Single-Variant Exome Association Results

### Significant Variants (p < `r params$exome_sig_threshold`)
```{r significant-single, echo=FALSE, message=FALSE, warning=FALSE}
# Filter significant variants
significant_variants <- single_variant %>% 
    filter(!is.na(LOG10P), LOG10P > exome_sig_log10p) %>%
    arrange(desc(LOG10P)) %>%
    select(CHROM, GENPOS, ID, ALLELE1, A1FREQ, BETA, SE, LOG10P, PVAL, PVAL_ADJ, LOG10P_ADJ, OR)

if(nrow(significant_variants) > 0) {
    kable(significant_variants, 
          format = "html", digits = 4,
          col.names = c("Chr", "Pos", "Variant ID", "Alt", "Alt Freq", 
                       "Beta", "SE", "-log10(P)", "P-value", "FDR P", "-log10(FDR P)", "OR")) %>%
        kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
        column_spec(c(6, 8, 9), color = "red") %>%
        scroll_box(width = "100%", height = "400px")
} else {
    cat("**No variants reached exome-wide significance**")
}
```

### Manhattan Plot
```{r manhattan-plot, echo=FALSE, message=FALSE, warning=FALSE}
# Manhattan Plot with improved styling
chrom_colors <- rep(c("#2E86AB", "#FF6B35"), length.out = length(unique(single_variant$CHROM)))

manhattan_plot <- ggplot(single_variant, aes(x = POS_INDEX, y = LOG10P, color = CHROM)) +
    geom_point(alpha = 0.7, size = 0.8) +
    scale_color_manual(values = chrom_colors) +
    labs(title = "Manhattan Plot: Single-Variant Exome Association",
         subtitle = paste("Total variants:", nrow(single_variant), 
                         "| Exome-wide significance threshold: p <", params$exome_sig_threshold),
         x = "Genomic Position", y = "-log10(p-value)") +
    geom_hline(yintercept = exome_sig_log10p, color = "red", linetype = "dashed", size = 0.8) +
    theme(legend.position = "none",
          plot.title = element_text(size = 14, face = "bold"),
          plot.subtitle = element_text(size = 10, color = "gray50"))

print(manhattan_plot)
```

### QQ Plot
```{r qq-plot, echo=FALSE, message=FALSE, warning=FALSE}
# QQ Plot for single variant p-values
qq_data <- single_variant %>%
    filter(!is.na(LOG10P)) %>%
    arrange(desc(LOG10P)) %>%
    mutate(
        observed = sort(LOG10P, decreasing = TRUE),
        expected = sort(-log10(ppoints(length(LOG10P))), decreasing = TRUE)
    )

# Calculate lambda GC correctly
chisq <- qchisq(1 - single_variant$PVAL, 1)
lambda_gc <- median(chisq, na.rm = TRUE) / qchisq(0.5, 1)

qq_plot <- ggplot(qq_data, aes(x = expected, y = observed)) +
    geom_point(alpha = 0.6, color = "#2E86AB") +
    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
    labs(title = "Q-Q Plot: Single-Variant P-values",
         subtitle = paste("Lambda GC:", round(lambda_gc, 3), 
                         "| Note: Inflation metrics are less interpretable in ExWAS due to sparse, low-frequency variant testing"),
         x = "Expected -log10(p-value)", 
         y = "Observed -log10(p-value)") +
    theme(plot.title = element_text(size = 14, face = "bold"),
          plot.subtitle = element_text(size = 10, color = "gray50"))

print(qq_plot)
```

## Gene-Based Burden Testing Results

### Summary by Mask
```{r mask-summary, echo=FALSE, message=FALSE, warning=FALSE}
# Summary statistics per mask
mask_summary <- gene_based %>%
  group_by(MASK) %>%
  summarize(
    Genes_Tested = n(),
    Significant_Genes = sum(PVAL_ADJ < params$fdr_threshold, na.rm = TRUE),
    Most_Significant_Gene = GENE[which.max(LOG10P)],
    Max_Log10P = max(LOG10P, na.rm = TRUE),
    Mean_Beta = mean(BETA, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    Significance_Rate = Significant_Genes / Genes_Tested * 100,
    Mask_Label = case_when(
      MASK == "M1" ~ "M1 (Pathogenic only)",
      MASK == "M2" ~ "M2 (Pathogenic + VUS)",
      TRUE ~ MASK
    )
  ) %>%
  select(Mask_Label, Genes_Tested, Significant_Genes, Most_Significant_Gene, 
         Max_Log10P, Mean_Beta, Significance_Rate)

kable(mask_summary, format = "html", digits = 3,
      col.names = c("Mask", "Genes Tested", "FDR Significant", "Top Gene", 
                    "Max -log10(P)", "Mean Beta", "Significance Rate (%)")) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, bold = TRUE)
```

### Top Genes by Clinical Category

#### M1 (Pathogenic variants only)
```{r top-genes-m1, echo=FALSE, message=FALSE, warning=FALSE}
# M1 (Pathogenic) - Top 10 genes
m1_top <- gene_based %>%
  filter(MASK == "M1") %>%
  slice_max(LOG10P, n = 50) %>%
  select(GENE, THRESH, BETA, SE, LOG10P, PVAL, PVAL_ADJ, OR) %>%
  arrange(desc(LOG10P))

if(nrow(m1_top) > 0) {
  kable(m1_top, format = "html", digits = 4,
        col.names = c("Gene", "MAF Filter", "Beta", "SE", "-log10(P)", "P-value", "FDR P-value", "OR")) %>%
    kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = TRUE) %>%
    column_spec(c(3, 5, 6), color = "red") %>% 
    scroll_box(width = "100%", height = "400px")
} else {
  cat("No results")
}
```

#### M2 (Pathogenic + VUS combined)
```{r top-genes-m2, echo=FALSE, message=FALSE, warning=FALSE}
# M2 (Pathogenic + VUS) - Top 10 genes
m2_top <- gene_based %>%
  filter(MASK == "M2") %>%
  slice_max(LOG10P, n = 50) %>%
  select(GENE, THRESH, BETA, SE, LOG10P, PVAL, PVAL_ADJ, OR) %>%
  arrange(desc(LOG10P))

if(nrow(m2_top) > 0) {
  kable(m2_top, format = "html", digits = 4,
        col.names = c("Gene", "MAF Filter", "Beta", "SE", "-log10(P)", "P-value", "FDR P-value", "OR")) %>%
    kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = TRUE) %>%
    column_spec(c(3, 5, 6), color = "red") %>% 
    scroll_box(width = "100%", height = "400px")
} else {
  cat("No results")
}
```

### Suggestive Gene-Based Associations (Raw p < 0.001, FDR ≥ `r params$fdr_threshold`)
```{r suggestive-genes, echo=FALSE, message=FALSE, warning=FALSE}
# Get genes with strong raw p-value but not FDR significant
suggestive_genes <- gene_based %>%
  filter(LOG10P > 3, PVAL_ADJ >= params$fdr_threshold) %>%  # p < 0.001, FDR >= threshold
  arrange(desc(LOG10P)) %>%
  slice_head(n = 15) %>%
  select(GENE, MASK, THRESH, BETA, LOG10P, PVAL, PVAL_ADJ, OR)

if(nrow(suggestive_genes) > 0) {
    cat("**Genes with strong evidence (raw p < 0.001) but not FDR significant**\n\n")
    kable(suggestive_genes,
          format = "html", digits = 4,
          col.names = c("Gene", "Mask", "Threshold", "Beta", "-log10(P)", 
                       "P-value", "FDR P-value", "OR")) %>%
        kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
        column_spec(1, bold = TRUE) %>%
        column_spec(c(4, 8), color = "orange") %>% 
      scroll_box(width = "100%", height = "400px")
} else {
    cat("**No suggestive associations found**")
}
```

### Volcano Plot by Mask
```{r volcano-plot, echo=FALSE, message=FALSE, warning=FALSE}
# Volcano Plot with FDR significance, faceted by mask
gene_based_plot <- gene_based %>%
  mutate(Significant = PVAL_ADJ < params$fdr_threshold,
         Mask_Label = case_when(
           MASK == "M1" ~ "M1 (Pathogenic only)",
           MASK == "M2" ~ "M2 (Pathogenic + VUS)",
           TRUE ~ MASK
         ))

# Get top FDR significant genes for labeling (top 5 per mask)
top_hits <- gene_based_plot %>% 
  filter(Significant) %>%
  group_by(MASK) %>%
  slice_max(LOG10P, n = 5) %>%
  ungroup()

gene_based_plot <- gene_based_plot %>%
  mutate(Label = ifelse(GENE %in% top_hits$GENE, GENE, NA))

# Calculate FDR cutoff for the line
fdr_cutoff <- min(gene_based$LOG10P[gene_based$PVAL_ADJ < params$fdr_threshold], na.rm = TRUE)
if(is.infinite(fdr_cutoff)) fdr_cutoff <- NA

volcano_plot <- ggplot(gene_based_plot, aes(x = BETA, y = LOG10P, color = Significant)) +
  geom_point(alpha = 0.6, size = 1.2) +
  {if(!is.na(fdr_cutoff)) geom_hline(yintercept = fdr_cutoff, linetype = "dashed", 
                                      color = "blue", alpha = 0.7)} +
  geom_vline(xintercept = 0, linetype = "dotted", color = "grey40") +
  geom_text_repel(aes(label = Label), size = 2.5, max.overlaps = 5, 
                  box.padding = 0.3, point.padding = 0.1) +
  scale_color_manual(values = c("gray60", "red"), 
                     labels = c("Not Significant", paste("FDR <", params$fdr_threshold))) +
  labs(title = "Volcano Plot: Gene-Based Burden Testing by Mask",
       subtitle = paste("FDR significant genes:", sum(gene_based_plot$Significant)),
       x = "Effect Size (Beta)",
       y = "-log10(p-value)",
       color = "Significance") +
  facet_wrap(~Mask_Label, scales = "free_y") +
  theme(plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 10, color = "gray50"),
        legend.position = "bottom",
        strip.text = element_text(size = 12, face = "bold"))

print(volcano_plot)
```


### CHEK2 Gene Analysis
```{r chek2-analysis,echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
chek2_results <- gene_based %>%
  filter(GENE == "CHEK2") %>%
  select(GENE, MASK, THRESH, CHROM, GENPOS, ALLELE1, A1FREQ, BETA, OR, SE, LOG10P, PVAL, PVAL_ADJ, LOG10P_ADJ) %>%
  arrange(MASK, THRESH)

if(nrow(chek2_results) > 0) {
  cat("**CHEK2 Gene Results (Chr22):**\n\n")
  
  chek2_file <- file.path(params$output_dir, paste0(params$project, "_chek2_results.csv"))
  write_csv(chek2_results, chek2_file)
  
  # Create color vector
  cell_colors <- ifelse(is.na(chek2_results$PVAL_ADJ), "gray",
                        ifelse(chek2_results$PVAL_ADJ < 0.05, "red", "black"))
  
  # Table goes here (will display properly)
  kable(chek2_results, 
        format = "html", digits = 4,
        col.names = c("Gene", "Mask", "Threshold", "Chr", "Pos", "Alt Allele", "Alt Freq", 
                     "Beta", "OR", "SE", "-log10(P)", "P-value", "FDR P-value", "-log10(FDR P)")) %>%
    kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
    column_spec(c(8, 11, 12), color = cell_colors) %>%
    scroll_box(width = "100%", height = "400px")
} else {
  cat("**CHEK2 gene not found in results**")
}
```


## Risk-Increasing Genes (Beta > 0)
```{r risk-genes, echo=FALSE, message=FALSE, warning=FALSE}
# Risk-increasing genes (positive associations)
risk_genes <- gene_based %>%
  filter(PVAL_ADJ < params$fdr_threshold, BETA > 0) %>%
  select(GENE, MASK, THRESH, BETA, PVAL_ADJ, OR) %>%
  arrange(PVAL_ADJ)

if(nrow(risk_genes) > 0) {
    cat("**Found", nrow(risk_genes), "risk-increasing gene associations**\n\n")
    kable(risk_genes,
          format = "html", digits = 4,
          col.names = c("Gene", "Mask", "MAF Filter", "Beta", "FDR P-value", "OR")) %>%
      kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"),
                    font_size = 11) %>%
      column_spec(1, bold = TRUE) %>%
      column_spec(c(4, 5), color = "red") %>% 
      scroll_box(width = "100%", height = "400px")

} else {
    cat("No risk-increasing gene associations found")
}

# Summary count
risk_count <- gene_based %>%
  filter(PVAL_ADJ < params$fdr_threshold) %>%
  summarise(Risk_Increasing = sum(BETA > 0, na.rm = TRUE),
            Protective = sum(BETA < 0, na.rm = TRUE))

if(nrow(risk_count) > 0 && risk_count$Risk_Increasing > 0) {
  cat("\n\n**Summary:**", risk_count$Risk_Increasing, "risk-increasing vs",
      risk_count$Protective, "protective associations")
}
```

## Output Files
```{r save-results, echo=FALSE, message=FALSE, warning=FALSE}
# Save ALL results to CSV files in output directory
# Create output directory if it doesn't exist
dir.create(params$output_dir, recursive = TRUE, showWarnings = FALSE)

single_file <- file.path(params$output_dir, paste0(params$project, "_single_variant_results.csv"))
gene_file <- file.path(params$output_dir, paste0(params$project, "_gene_based_results.csv"))

write_csv(single_variant, single_file)
cat("**All single variant results saved to:** `", single_file, "`\n\n")

# Save gene-based results ordered by LOG10P
gene_based_ordered <- gene_based %>% arrange(desc(LOG10P))
write_csv(gene_based_ordered, gene_file)
cat("**All gene-based results (ordered by -log10P) saved to:** `", gene_file, "`\n\n")

# Save M1 results (all columns, ordered by LOG10P)
m1_all <- gene_based %>%
  filter(MASK == "M1") %>%
  group_by(MASK) %>% 
  arrange(desc(LOG10P))

if(nrow(m1_all) > 0) {
  m1_file <- file.path(params$output_dir, paste0(params$project, "_M1_gene_based_results.csv"))
  write_csv(m1_all, m1_file)
  cat("**M1 (Pathogenic only) results (ordered by -log10P) saved to:** `", m1_file, "`\n\n")
}

# Save M2 results (all columns, ordered by LOG10P)
m2_all <- gene_based %>%
  filter(MASK == "M2") %>%
  arrange(desc(LOG10P))

if(nrow(m2_all) > 0) {
  m2_file <- file.path(params$output_dir, paste0(params$project, "_M2_gene_based_results.csv"))
  write_csv(m2_all, m2_file)
  cat("**M2 (Pathogenic + VUS) results (ordered by -log10P) saved to:** `", m2_file, "`\n\n")
}

# Save significant results if any exist
if(nrow(significant_variants) > 0) {
    sig_single_file <- file.path(params$output_dir, paste0(params$project, "_significant_single_variants.csv"))
    write_csv(significant_variants, sig_single_file)
    cat("**Significant single variants saved to:** `", sig_single_file, "`\n\n")
}

if(exists("suggestive_genes") && nrow(suggestive_genes) > 0) {
    sig_gene_file <- file.path(params$output_dir, paste0(params$project, "_suggestive_genes.csv"))
    write_csv(suggestive_genes, sig_gene_file)
    cat("**Suggestive gene associations saved to:** `", sig_gene_file, "`\n\n")
}

cat("**Analysis completed on:**", format(Sys.time(), "%Y-%m-%d %H:%M:%S"))
```
